The Mechanism of Shrimpoluminescence

### 2022-01-14 sonoluminescence/paper/paper.tex
sdfadsfa

\documentclass[rmp,aps,nofootinbib,superscriptaddress,floatfix]{revtex4-2} 
\usepackage{graphicx}
\usepackage{xcolor} 
\usepackage{amsmath}
\usepackage{amssymb} 
\usepackage{natmove}
\usepackage{natbib}
\usepackage{hyperref} 
\usepackage{bm}
\bibliographystyle{apsrev4-2}
\setcitestyle{numbers,square}

@@

\title{On the Origin of Shrimpoluminescence}

@@

\begin{abstract}
shrimpity shrimp shrimp shrimp. abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract 
\end{abstract}

@@

%\listoffigures
%\listoftables
%\tableofcontents

%\emph{Frequently Used Abbreviations}
%\begin{itemize}
%    \item SL: sonoluminescence
%    \item SBSL: single-bubble sonoluminesence
%    \item MBSL: multi-bubble sonoluminescence
%\end{itemize}

\section{Introduction}
Snapping shrimp, like our cute friend in Fig. \ref{fig:shrimp} (left), have long been known to produce cavitating bubbles by \emph{snapping} their claws \cite{versluis2000snapping,lohse2001snapping,tang2019bioinspired}. They have a strong appendage (the \emph{dactyl}) in their claw [Fig. \ref{fig:shrimp} (center)] that is used to create a very high-velocity jet of water. The low pressure region in the jet's wake forms a bubble [Fig. \ref{fig:shrimp} (right)] that, among other things, produces an exceptionally loud noise when it collapses. The sound (i.e. the pressure wave) produced by even a \emph{single} shrimp's snap is detectable over a mile away \cite{everest1948acoustical}. The noise produced by groups of shrimp is so intense that the U.S. Navy used them as ``sonar-camouflage" in the Pacific ocean during World War II \cite{versluis2000snapping}.

@@

The shrimp were not patriots helping the war-effort, however; they snapped for food. The shock-wave produced by the cavitating bubble is used to stun and even kill prey \cite{versluis2000snapping}. If the shrimp's prey had very\footnote{We stress \emph{very}: shrimpoluminescence is too weak to be seen by the naked-eye.} sensitive eyes (and also were not dead) they might notice a flash of light is also produced through an effect referred to as ``shrimpoluminescence" in the case of the pistol shrimp \cite{lohse2001snapping}, but more generally known as \emph{sonoluminescence}.

Sonoluminescence (SL) is more precisely defined as the process by which a ``driven gas bubble collapses so strongly that the energy focusing at collapse leads to light emission" \cite{brenner2002single}. SL comes in two forms: (i) single-bubble sonoluminescence and (ii) multi-bubble sonoluminescence. The distinction is self-explanatory: multi-bubble sonoluminescence (MBSL) consists of  ``the simultaneous creation and destruction of many separate, individual cavitation bubbles" \cite{crum1994sonoluminescence,brenner2002single}, whereas in single-bubble sonoluminescence (SBSL), rather obviously, only a single bubble is present \cite{gaitan1992sonoluminescence}. The discovery of MBSL predates SBSL by $\sim$60 years but due to the more-or-less random and fleeting nature of the bubbles, SL in general wasn't well studied until the early 1990's when it was discovered that single bubbles could be created and periodically driven to produce light with very high precision \cite{crum1994sonoluminescence,gaitan1990experimental,gaitan1992sonoluminescence,brenner2002single}. In SBSL, emission from a single bubble is not complicated from multiple scattering (off other bubbles), volumetric-light emission from the bubble cloud, etc. Similarly, the bubble is not perturbed by interaction with other bubbles and, due to its tiny size, by interaction with the container walls. As a result, the theory is greatly simplified compared to MBSL. It is not an exaggeration to say that nearly all theoretical and experimental progress to explain SL has been made using SBSL, with some authors even calling it ``the hydrogen atom of SL" \cite{lohse2018bubble,crum1994sonoluminescence}.

\begin{figure}
\includegraphics[width=0.6\linewidth]{figs/pulses}
    \caption{\cite{brenner2002single,crum1994sonoluminescence}}
\label{fig:pulses}
\end{figure}

Studying SBSL, while offering advantages, also comes with complications. Due to the tiny volume of the bubble, directly measuring the temperature or pressure \emph{inside} the bubble is practically impossible \cite{suslick2008inside}. Still, the discovery of SBSL created a rush of effort to explain the phenomena with arguments ranging from the simplest models \footnote{There are far too many to try list here and we will not be interested in the vast majority of early models which are now irrelevant. References to these can be found in Gaitan \cite{gaitan1990experimental} and Brenner et al. \cite{brenner2002single}.} to more exotic explanations based of quantum field theory \cite{schwinger1993casimir,eberlein1996sonoluminescence,liberati2000sonoluminescence}. Over time, the \emph{phase-space} of SBSL has been refined: SBSL only occurs for a narrow range of driving pressures and for a particular combination of host-liquid and gas content in the bubble. The mapping of the phase-space of SBSL is a very rich subject and merits a review in itself (several exist \cite{brenner2002single,yasui2018acoustic}). We will not pursue this; our goal in this paper is to explain \emph{shrimpoluminescence} so we will mainly focus on SBSL as it occurs in \emph{water} containing \emph{air bubbles}, though occasionally we will comment on SBSL in other fluids.

Let us now sketch the SBSL process a little more precisely. An air bubble is trapped at the center of an acoustically driven flask containing a fluid. The pressure wave in the fluid, shown as a function of time in Fig. \ref{fig:pulses}, drives the expansion and contraction of the bubble and, in turn, the dynamics of the gas in the bubble responds to the bubble's oscillations. Within the phase-space relevant to SBSL, we get the very complicated non-linear response of the bubble's radius as shown in Fig. \ref{fig:pulses}. Let's see how these dynamics lead to SBSL.

First, as the pressure decreases and becomes negative, the bubble expands gradually: surface tension and the negative pressure in the bubble tend to slow this down. Eventually the pressure is increasing again. Once it becomes positive, the bubble violently collapses to its minimum radius: during compression, the negative pressure in the bubble is very large and works with the driving pressure to rapidly accelerate the bubble's wall. Since the collapse is so quick, the bubble's contents are adiabatically compressed, resulting in very large temperature and pressure in the bubble. If everything is just right, the temperature and pressure are large enough for a burst of light to be produced as shown by the bottom curve in Fig. \ref{fig:pulses}. After the collapse, there is a period of \emph{after-bouncing} that continues until the pressure is negative again.

It turns out that the light pulse is very short (only $\sim0.003\%$ of the bubble's cycle \cite{suslick2008inside}) and its spectrum depends sensitively on both the mechanical and chemical properties of the host-liquid and gas in the bubble, as well as the driving pressure and frequency \cite{brenner2002single,suslick2008inside}. The mechanical properties determine the pressure and temperature inside the bubble which in turn control chemical reactions: all of these data are used to explain the light emission. For extreme enough conditions in the bubble, which occur only briefly, molecular dissociation and recombination, atomic/excited-state transitions, and electron-ion/electron-neutral atom bremsstrahlung are possible \cite{an2009diagnosing,an2008spectral,an2006mechanism,flannigan2005plasma,suslick2008inside,flannigan2006measurement}. These are now known to be the processes which emit light \cite{lohse2018bubble,yasui2018acoustic}.

Our goal in this paper is to present the simplest theory needed to understand \emph{shrimpoluminescence}, though we will actually concentrate on the related physics of a bubble undergoing SBSL in the lab as it is apparently simpler to create and characterize SBSL without involving shrimp \footnote{ For example, convincing the shrimp to snap requires tickling them \cite{lohse2001snapping,versluis2000snapping,lohse2018bubble}. Besides notable exceptions \cite{tang2019bioinspired}, practically all work to study SL has not involved shrimp.}. Firstly, we will look at the problem of the fluid containing the bubble; we will derive the equations of motion for the bubble's wall. Nextly, we will use our results for the bubble's wall to understand the dynamics of the gas trapped in the bubble. The result of this will turn out to be an estimate of the \emph{temperature} and \emph{pressure} in the bubble. We will then look at theories presenting the origin of light from the very hot contents of the bubble. For relatively mild conditions inside the bubble, most light emission occurs during molecular dissociation processes \cite{}. These are the conditions in e.g. weakly driven 85\% H$_2$SO$_4$. In water, the pressure in the bubble is considerably higher and most light emission is due the electron-ion and electron-neutral atom bremsstrahlung which occur at higher temperatures \cite{flannigan2005plasma,an2009diagnosing,suslick2008inside}. Recalling that we want to understand SBSL in water, we will mainly focus on these latter processes. Moreover, throughout the course of our journey, we will stick to the simplest results that still contain the essential physics we need. Connections to more advanced treatments, and their implications, are provided for completeness.

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{figs/flask.pdf}
    \caption{(a) Schematic of a spherical acoustic levitation cell. The piezoelectric transducers that drive the bubble trapped in the flask are labeled in the diagram. (b) Photograph of the same. Here, the fluid is aqueous H$_2$SO$_4$ instead of water. A sonoluminescing bubble is clearly visible in the center of the flask. The photo was taken in a fully lit room with exposure time 2 s. (c) Schematic of a Mie scattering experimental setup. A similar acoustic levitation cell as (a) is shown with an added laser source and photomultiplier tubes (PMT) to analyze the scattered and emitted light. (a), (b), and (c) are from refs. \cite{brenner2002single}, \cite{suslick2008inside}, and \cite{gompf2000mie} respectively.}
\label{fig:flask}
\end{figure}

@@

SBSL, unlike previous studies on MBSL, allowed very precise control and measurement of the SL process. With unprecedented experimental control, many discrepancies in previous assumptions about SL were discovered. Experiments measuring the duration of the light pulse found that it was orders or magnitude smaller than the time in which the bubble was compressed to its smallest radius \cite{barber1992resolving,barber1991observation}. This discovery implied that SL was nearly decoupled from the bubble's dynamics. New models were proposed based on \emph{converging shock waves} at the bubble's center with estimates of the temperature at the center of bubbles $\sim10^8$ K \cite{wu1993shock,greenspan1993sonoluminescence}. At the same time, experimentalists fit the bubble's light emission spectra as a \emph{black body emitter} and concluded that the temperature in the bubble was at least 25,000 K \cite{hiller1992spectrum}.

These very high estimates for the temperature in the bubbles led to a spark of interest more broadly: if the temperature in the bubble were really that large, then it should be possible for nuclear \emph{fusion} to occur \cite{}. An action movie featuring Keanu Reeves was even made with this at the center of the plot \footnote{It is called \emph{Chain Reaction} and I am unwilling to watch it.}. In the early 2000's, several papers were even published claiming that stable nuclear fusion was possible in the lab using a method based on SBSL \cite{}. Unfortunately these results turned out to be fraudulent \cite{}. Shortly after this fiasco, evidenced emerged that there are shape instabilities in the bubbles dynamics indicating that the converging shock-wave hypothesis is probably not right. This severely reduced the estimates for the temperature to $\sim 10,000$ K, ruling out the possibility of fusion occurring at all \cite{}. Moreover, it was shown that the light is most likely emitted from the \emph{bulk} of the bubble as opposed to its surface, making fits to a black body spectrum (i.e. surface emission) incorrect \cite{}. Current estimates for the temperature, which we will study in the rest of this paper, put the center of a sonoluminescing bubble at $10,000-30,000$ K \cite{flannigan2005plasma,suslick2008inside,yasui2018acoustic,an2009diagnosing,an2008spectral,an2006mechanism}.

\section{Bubble Dynamics}
In this section, we will present the theory needed to model and understand the dynamics of a bubble undergoing SBSL. We will split this into parts. Firstly, we will derive the equations of motion for the bubble's wall. Nextly, we will review some important experimental developments that we will then use to argue for a simple model for the dynamics of the gas in the bubble. Lastly, we will compare results of a simulated bubble to experimental data. The connection to experiment will be what allows us to calculate the temperature in real bubbles.

\subsection{The Bubble Wall}
As it turns out, the dynamics of the bubble in SBSL (regardless of the light emission) are quite well described both qualitatively and \emph{quantitatively} by the classical theory of bubble dynamics \cite{prosperetti1999old,brenner2002single,prosperetti1986bubble,plesset1977bubble,suslick2008inside,yasui2018acoustic,brennen2014cavitation}. This isn't particularly surprising since the light emission and bubble collapse occur at different timescales (the duration of maximum compression's is $\sim 0.003\%$ of the bubble's period) \cite{suslick2008inside,prosperetti1999old,brenner2002single,prosperetti1986bubble,plesset1977bubble}. The starting point for any theory of the bubble dynamics is Rayleigh's original work \cite{rayleigh1917pressure}, now expounded upon by many others. The most widely known modern work is that of Plesset \cite{plesset1977bubble,plesset1949dynamics,prosperetti1986bubble}, resulting in the so called ``the Rayleigh-Plesset" (RP) equation. The derivation assumes the host liquid is incompressible, ultimately resulting in us neglecting the effects of sound radiated by the bubble. Corrections exist that improve upon the RP equation in various ways and we will discuss these below \cite{}. However, for brevity's sake, we will only derive the RP equation here and merely quote the others as they are very similar in form to the RP equation. The field of \emph{bubble dynamics} is quite mature and attempting to review it here would be out of scope of this paper; instead, the reader is referred to numerous books and reviews \cite{prosperetti1999old,brenner2002single,yasui2018acoustic,prosperetti1986bubble}.

The RP equation can be deduced from the \emph{Navier-Stokes} (NS) equations \footnote{The NS equations are derived in the appendix} \cite{prosperetti1999old,brenner2002single,prosperetti1986bubble,plesset1977bubble,suslick2008inside,yasui2018acoustic}. The NS equations for a compressible fluid are
\begin{equation}
\begin{split}
    \rho \frac{d \bm{u}}{dt} = \rho \left[ \partial_t \bm{u}+\left(\bm{u}\cdot \nabla \right)\bm{u} \right] & =-\nabla p + \eta \nabla \left(\nabla \cdot \bm{u} \right)+\mu \nabla^2 \bm{u} + \bm{f}_B \\ 
     \partial_t \rho+\nabla\cdot(\rho \bm{u}) & = 0.
     \label{eq:NS_equations}
\end{split}
\end{equation}

Here, $\bm{u}(\bm{x},t)$ is the velocity of a fluid parcel at position $\bm{x}$ at time $t$, $\rho (\bm{x},t)$ is the fluid's density, $p$ is the pressure, $\eta \equiv \left(\xi + \frac{2}{3}\mu \right)$ is the \emph{bulk} viscosity with $\mu$ the \emph{shear} viscosity, and $\bm{f}_B$ are \emph{body} forces (e.g. gravity, electrostatic forces) which are usually from external sources and will be assumed negligible from here on. The subscripts on $\partial$ denote what derivative is being taken and $\nabla$ and $\nabla^2$ have their usual meanings. The first equation is \emph{conservation of momentum} for the fluid, i.e. Newton's $2^{nd}$ law; the second equation is \emph{mass conservation}. The total-derivative of a moving fluid $\frac{d}{dt}\equiv D_t$ is sometimes called the \emph{material derivative}. In the case of velocity $D_t \bm{u}$ is the \emph{acceleration} of the fluid. It records not only explicit time dependence of the fluid's velocity $\partial_t \bm{u}$ but also how the fluid's velocity varies \emph{in space} as it moves past us: $\left( \bm{u}\cdot\nabla \right) \bm{u}$. The pressure term on the right hand side is to be understood as forces from the \emph{elastic} energy. On the other hand, the terms $\sim \bm{u}$ are viscous (damping) terms that tend to make the velocity field spatially uniform: they vanish when the (spatial) derivatives of the velocity vanish. The bulk-viscosity term $\sim \eta$ damps radial changes in the fluids velocity (e.g. dilation/contraction) while the shear-viscosity term $\sim\mu$ resists shearing.

Solving eqs. \ref{eq:NS_equations} is an intractable problem. To make progress, we will make some drastic approximations that are more-or-less valid for our problem. Firstly, we will assume irrational flow (i.e. $\nabla\times\bm{u}\equiv 0$) so that there is only radial motion in the liquid (i.e. $\bm{u}=u\bm{r}$). Note that, since the flow is assumed irrotational, we can represent the velocity as the gradient of a scalar function: $u\bm{r}=\partial_r \phi \bm{r}$ \cite{jackson1999classical}. This amounts to assuming that the bubble is always spherical which seems like a rather drastic approximation but has been validated experimentally in many cases \cite{}. The fact that the bubble tends to remain spherical can be understood by accounting for surface-tension at the liquid-bubble interface \cite{prosperetti1999old}.

Nextly, we assume that the viscous terms are negligible in the bulk dynamics of the liquid. For (relatively) low viscosity fluids such as water which is also nearly incompressible, this is an accurate approximation and is widely used \cite{prosperetti1986bubble,prosperetti1999old,brenner2002single,plesset1977bubble}.  We will account, to some extent, for viscosity later when looking at the bubble-liquid interface. Moreover, we are assuming that the flow is \emph{isentropic}, i.e. that it is reversible (no damping) and that no heat is exchanged between fluid parcels. We will further assume that the liquid is isothermal, i.e. its temperature is constant (in space). Then pressure $p$ is determined from an instantaneous equation-of-state $p=p(\rho,T)$. In the case of SBSL, this is valid since the bubble makes up a \emph{tiny} fraction of the total volume and, as we will later see, heat-transport across the liquid-bubble interfacing is usually neglected anyway (i.e. the bubble is compressed adiabatically in the thermodynamic sense \footnote{According to Wikipedia, \emph{adiabatic} means \emph{fast} in thermodynamics lingo. This is relevant to us since we are claiming the bubble wall moves so quickly that it is compressed to its maximum pressure before any heat can flow out. On the other hand, the mechanics lingo implies \emph{adiabatic} to mean \emph{slow}. This is, e.g. the adiabatic theorem in quantum mechanics: a perturbation acts so slowly that the system is in its ground state at all times.})

Lastly, related to the fact that the bubble is tiny, we assume that the extent of the liquid is so large compared to the bubble that we may consider the dynamics of the liquid as if there were no bubble present; similarly, we consider the dynamics of a bubble in an infinite, isotropic medium. Of course the bubble-liquid interface enters both systems as a boundary condition \cite{prosperetti1986bubble}.

>>>>

\documentclass[prb,aps,nofootinbib,superscriptaddress,floatfix]{revtex4-2} 
\usepackage{graphicx}
\usepackage{xcolor} 
\usepackage{amsmath}
\usepackage{amssymb} 
\usepackage{natmove}
\usepackage{natbib}
\usepackage{hyperref} 
\usepackage{bm}

@@

\title{The Mechanism of Shrimpoluminescence}

@@

\begin{abstract}
Snapping shrimp can produce bubbles that emit light when they collapse. The light emission is known as \emph{shrimpoluminescence} in the case of shrimp, but more generally when an acoustically driven bubble emits light, it is called \emph{sonoluminescence}. We would like to understand how the light is emitted. In this paper, we will specialize to the case of a single, stable bubble driven to produce light over many cycles. We will derive the bubble's equation of motion and examine the conditions in its interior. It turns out that, when the bubble collapses in a process known as \emph{cavitation}, the gas trapped in the bubble becomes hot enough to ionize. Light is emitted as black-body radiation with electron-ion bremsstrahlung, electron-atom bremsstrahlung, and electron-ion recombination limiting the amount of light that escapes the bubble.
\end{abstract}

@@

\section{Introduction}
Snapping shrimp, like our cute friend in fig. \ref{fig:shrimp}, are known to produce cavitating bubbles by snapping their claws \cite{versluis2000snapping,lohse2001snapping,tang2019bioinspired}. They have a strong appendage (the \emph{dactyl}) in thier claw (fig. \ref{fig:shrimp} [center]) that is used to create a high-velocity jet of water. The low pressure region in the jet's wake forms a bubble (fig. \ref{fig:shrimp} [right]) that produces an exceptionally loud noise when it collapses. The sound produced by even one shrimp's snap is detectable over a mile away \cite{everest1948acoustical}. The noise produced by groups of shrimp is so intense that the U.S. Navy used them as ``sonar-camouflage" in the Pacific ocean during World War II \cite{versluis2000snapping}. The shrimp were not patriots helping the war-effort, however; they snapped for food. The sound wave produced by the cavitating bubble is used to stun or kill prey \cite{versluis2000snapping}. If the shrimp's prey had very\footnote{Shrimpoluminescence is too weak to be seen by the naked-eye.} sensitive eyes (and also were not dead) they might notice a flash of light is also produced through an effect referred to as ``shrimpoluminescence" in the case of the pistol shrimp \cite{lohse2001snapping}, but more generally known as \emph{sonoluminescence}.

@@

Sonoluminescence (SL) is defined as the process by which a ``driven gas bubble collapses so strongly that the energy focusing at collapse leads to light emission" \cite{brenner2002single}. SL comes in two forms: (i) single-bubble sonoluminescence and (ii) multi-bubble sonoluminescence. Multi-bubble sonoluminescence (MBSL) consists of  ``the simultaneous creation and destruction of many separate, individual cavitation bubbles" \cite{crum1994sonoluminescence,brenner2002single}, whereas in single-bubble sonoluminescence (SBSL), rather obviously, only a single bubble is present \cite{gaitan1992sonoluminescence}. The discovery of MBSL predates SBSL by $\sim$60 years but due to the random and fleeting nature of the bubbles, SL wasn't well studied until the early 1990's when it was discovered that single bubbles could be created and periodically driven to produce light with very high precision \cite{crum1994sonoluminescence,gaitan1990experimental,gaitan1992sonoluminescence,brenner2002single}. In SBSL, emission from a single bubble is not complicated from scattering off other bubbles. Similarly, the bubble is not perturbed by interaction with other bubbles or, due to its tiny extent, by interaction with the container walls. The theory is greatly simplified compared to MBSL. It is not an exaggeration to say that nearly all progress to explain SL has been made using SBSL, with some authors even calling it ``the hydrogen atom of SL" \cite{lohse2018bubble,crum1994sonoluminescence}. The discovery of SBSL created a rush of effort to explain the phenomena with arguments ranging from the simplest models \footnote{There are too many to try list and we won't be interested in most of them. References can be found in Gaitan \cite{gaitan1990experimental} and Brenner et al. \cite{brenner2002single}.} to more exotic explanations based of quantum field theory \cite{schwinger1992casimir1,schwinger1992casimir2,schwinger1993casimir1,schwinger1993casimir2,schwinger1993casimir3,schwinger1993casimir4,schwinger1994casimir,eberlein1996sonoluminescence,liberati2000sonoluminescence}.

\begin{figure}
\includegraphics[width=0.7\linewidth]{figs/pulses}
    \caption{Driving pressure, bubble radius, and SL intensity as a function of time for an air bubble in water. Note that the width of the light pulse at bubble collapse is \emph{very} short. From ref. \cite{crum1994sonoluminescence}}
\label{fig:pulses}
\end{figure}

Let us now sketch SBSL more precisely. An air bubble is trapped at the center of an acoustically driven flask containing a fluid. The pressure wave in the fluid, shown as a function of time as the top curve in fig. \ref{fig:pulses}, drives the expansion and contraction of the bubble and, in turn, the gas in the bubble responds to the bubble's oscillations. Under the right circumstances, we get the very complicated non-linear response of the bubble's radius shown as the middle curve in fig. \ref{fig:pulses}. Now let's see how these dynamics lead to SBSL.

First, as the pressure decreases and becomes negative, the bubble expands gradually: surface tension and the negative pressure in the bubble tend to slow this down. Eventually the pressure is increasing again. Once it becomes positive, the bubble violently collapses to its minimum radius: during compression, the negative pressure in the bubble is very large and works with the driving pressure to rapidly accelerate the bubble's wall. The collapse is so fast that the bubble's contents are adiabatically compressed, resulting in a very large temperature in the bubble. If everything is just right, the temperature is large enough that a pulse of light is produced as shown by the bottom curve in fig. \ref{fig:pulses}. After the collapse, there is a period of \emph{after-bouncing} that continues until the pressure is negative again.

It turns out that the light pulse is very short (only $\sim0.003\%$ of the bubble's cycle \cite{suslick2008inside}) and its spectrum depends sensitively on both the mechanical and chemical properties of the host-liquid and gas in the bubble, as well as the driving pressure and frequency \cite{brenner2002single,suslick2008inside}. The mechanical properties determine the pressure and temperature in the bubble which in turn control chemical reactions: all of these data are used to explain the light emission. For extreme enough conditions in the bubble, which occur only briefly, molecular dissociation and recombination, atomic/excited-state transitions, and electron-ion/electron-neutral atom bremsstrahlung are possible \cite{an2009diagnosing,an2008spectral,an2006mechanism,flannigan2005plasma,suslick2008inside,flannigan2006measurement}. These are now known to be the processes which emit light \cite{lohse2018bubble,yasui2018acoustic}.

Our goal in this paper is to present the simplest theory needed to understand shrimpoluminescence, though we will specialize to the related physics of a bubble undergoing SBSL in the lab as it is apparently simpler to create and characterize SBSL without involving shrimp\footnote{For example, convincing the shrimp to snap requires tickling them \cite{lohse2001snapping,versluis2000snapping,lohse2018bubble}. Besides notable exceptions \cite{tang2019bioinspired}, practically all work to study SL has not involved shrimp.}. Firstly, we will look at the problem of the fluid containing the bubble and derive the equations of motion for the bubble's wall. Nextly, we will use our results for the bubble's wall to understand the dynamics of the gas trapped in the bubble, estimate the \emph{temperature} and \emph{pressure} in the gas. We will then discuss theories presenting the mechanisms of light emission/absorption in the bubble which, combined with the temperature, allow use to calculate the bubbles light spectrum. Throughout the course of our journey, we will stick to the simplest results that still contain the essential physics we need. Connections to more advanced treatments, and their implications, are provided for completeness.

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{figs/flask.pdf}
    \caption{(a) Schematic of a spherical ``acoustic levitation cell". The piezoelectric transducers that drive the bubble trapped in the flask are labeled in the diagram. (b) Photograph of the same. Here, the fluid is aqueous H$_2$SO$_4$ instead of water. A sonoluminescing bubble is clearly visible in the center of the flask. The photo was taken in a fully lit room with exposure time 2 s. (c) Schematic of a Mie scattering experimental setup. A similar levitation cell as (a) is shown with an added laser source and photomultiplier tubes (PMT) to analyze the scattered and emitted light. (a), (b), and (c) are from refs. \cite{brenner2002single}, \cite{suslick2008inside}, and \cite{gompf2000mie} respectively.}
\label{fig:flask}
\end{figure}

@@

SBSL, unlike previous studies on MBSL, allowed very precise control and measurement of the SL process. With unprecedented experimental control, many discrepancies in previous assumptions about SL were discovered. Experiments measuring the duration of the light pulse found that it was orders or magnitude smaller than the time in which the bubble was compressed to its smallest radius \cite{barber1992resolving,barber1991observation}. This discovery implied that SL was nearly decoupled from the bubble's dynamics. New models were proposed based on \emph{converging shock waves} at the bubble's center with estimates of the temperature at the center of bubbles $\sim10^8$ K \cite{wu1993shock,greenspan1993sonoluminescence}. These very high estimates for the temperature in the bubbles led to a spark of interest more broadly: if the temperature in the bubble were really that large, then it should be possible for nuclear \emph{fusion} to occur \cite{}. An action movie featuring Keanu Reeves was made with this at the center of the plot \footnote{It is called \emph{Chain Reaction} and I am unwilling to watch it.}. and in the early 2000's, several papers were published claiming that stable nuclear fusion was possible in the lab using a method based on SBSL \cite{}. Unfortunately these results turned out to be fraudulent \cite{}. Eventually evidenced emerged that there are shape instabilities in the bubbles dynamics prohibiting converging shock-waves and severely reducing estimates for the temperature to $\sim 10,000$ K, ruling out the possibility of fusion occurring \cite{brenner2002single}. Current estimates for the temperature, which we will study in the rest of this paper, put the center of a sonoluminescing bubble between $10,000-30,000$ K \cite{flannigan2005plasma,suslick2008inside,yasui2018acoustic,an2009diagnosing,an2008spectral,an2006mechanism}.

\section{Bubble Dynamics}
In this section, we will present the theory needed to model and understand the dynamics of a bubble undergoing SBSL. We will split this into parts. Firstly, we will derive the equations of motion for the bubble's wall. Next, we will review some important experimental developments that we will then use to argue for a simple model for the dynamics of the gas in the bubble. Lastly, we will compare results of a simulated bubble to experimental data. The connection to experiment will be what allows us to calculate the temperature in real bubbles.

\subsection{The Bubble Wall}
It turns out the dynamics in SBSL are quite well described both qualitatively and quantitatively by \emph{the classical theory of bubble dynamics} \cite{prosperetti1999old,brenner2002single,prosperetti1986bubble,plesset1977bubble,suslick2008inside,yasui2018acoustic,brennen2014cavitation}. The starting point for the theory is Rayleigh's original work \cite{rayleigh1917pressure}, now expounded upon by many others. The most widely known modern work is that of Plesset \cite{plesset1977bubble,plesset1949dynamics,prosperetti1986bubble}, resulting in the so called ``the Rayleigh-Plesset" (RP) equation. The derivation assumes the host liquid is incompressible, ultimately resulting in us neglecting the effects of sound radiated by the bubble. Corrections exist that improve upon the RP equation in various ways and we will discuss this below. However, we will only derive the RP equation here and merely quote the others as they are similar in form. The field of bubble dynamics is quite mature and attempting to review it here would be out of scope of this paper; instead, the reader is referred elsewhere \cite{prosperetti1999old,brenner2002single,yasui2018acoustic,prosperetti1986bubble}.

The RP equation is deduced from the \emph{Navier-Stokes} (NS) equations \cite{prosperetti1999old,brenner2002single,prosperetti1986bubble,plesset1977bubble,suslick2008inside,yasui2018acoustic}. The NS equations for a compressible fluid are
\begin{equation}
\begin{split}
    \rho \frac{d \bm{u}}{dt} = \rho \left[ \partial_t \bm{u}+\left(\bm{u}\cdot \nabla \right)\bm{u} \right] & =-\nabla p + \eta \nabla \left(\nabla \cdot \bm{u} \right)+\mu \nabla^2 \bm{u} + \bm{f}_B \\ 
     \partial_t \rho+\nabla\cdot(\rho \bm{u}) & = 0.
     \label{eq:NS_equations}
\end{split}
\end{equation}

Here, $\bm{u}(\bm{x},t)$ is the velocity of a fluid parcel at position $\bm{x}$ at time $t$, $\rho (\bm{x},t)$ is the fluid's density, $p$ is the pressure, $\eta \equiv \left(\xi + 2\mu/3 \right)$ is the \emph{bulk} viscosity with $\mu$ the \emph{shear} viscosity, and $\bm{f}_B$ are body forces (e.g. gravity, electrostatic forces) which are usually from external sources and will be assumed negligible from here on. The subscripts on $\partial$ denote what derivative is being taken and $\nabla$ and $\nabla^2$ have their usual meanings. The first equation is conservation of momentum for the fluid, i.e. Newton's $2^{nd}$ law; the second equation is mass conservation. The total-derivative of a moving fluid $d/dt\equiv D_t$ is sometimes called the \emph{material derivative}. In the case of velocity $D_t \bm{u}$ is the acceleration of the fluid. It records not only explicit time dependence of the fluid's velocity $\partial_t \bm{u}$ but also how the fluid's velocity varies in space as it moves past us: $\left( \bm{u}\cdot\nabla \right) \bm{u}$. The pressure term on the right hand side is to be understood as forces from the elastic energy. On the other hand, the terms $\sim \bm{u}$ are viscous (damping) terms that tend to make the velocity field spatially uniform: they vanish when the (spatial) derivatives of the velocity vanish. The bulk-viscosity term $\sim \eta$ damps radial changes in the fluids velocity (e.g. dilation/contraction) while the shear-viscosity term $\sim\mu$ resists shearing.

Solving eqs. \ref{eq:NS_equations} is intractable. To make progress, we make some drastic approximations that are more-or-less valid for our problem. Firstly, we will assume irrational flow (i.e. $\nabla\times\bm{u}\equiv 0$) so that there is only radial motion in the liquid (i.e. $\bm{u}=u\bm{r}$). Since the flow is assumed irrotational, we can represent the velocity as the gradient of a scalar function: $u\bm{r}=\partial_r \phi \bm{r}$ \cite{jackson1999classical}. This amounts to assuming that the bubble is always spherical which seems like a rather drastic approximation but is validated experimentally. The fact that the bubble tends to remain spherical is understood by accounting for surface-tension at the liquid-bubble interface \cite{prosperetti1999old}.

Next, we assume that the viscous terms are negligible in the bulk dynamics of the liquid. For low viscosity fluids such as water which is also nearly incompressible, this is an accurate approximation \cite{prosperetti1986bubble,prosperetti1999old,brenner2002single,plesset1977bubble}. We will account for viscosity later when looking at the bubble-liquid interface. We will also assume \emph{isentropic} and \emph{isothermal} flow, i.e. no damping and no heat flow between fluid parcels. The pressure $p$ is then determined from an instantaneous equation-of-state $p=p(\rho,T)$. In the case of SBSL, this is valid since the bubble makes up a \emph{tiny} fraction of the total volume and any heat-transport across the liquid-bubble interfacing is negligible \cite{prosperetti1999old}.

Lastly, related to the fact that the bubble is tiny, we assume that the extent of the liquid is so large compared to the bubble that we may consider the dynamics of the liquid as if there were no bubble present; similarly, we consider the dynamics of a bubble in an infinite, isotropic medium. Of course the bubble-liquid interface enters both systems as a boundary condition.

With these simplifying assumptions (and a vector identity \footnote{$\left( \nabla \cdot \bm{u} \right) \bm{u} = \frac{1}{2} \nabla (u^2) - \bm{u}\times \left( \nabla \times \bm{u} \right)$}) we rewrite eqs. \ref{eq:NS_equations} as 
\begin{equation}
\begin{split}
     \partial_r \left[ \partial_t \phi +\frac{1}{2} \left( \partial_r \phi \right)^2 \right] & = - \frac{1}{\rho} \partial_r p  \\ 
     \partial_t \rho+ \partial_r \phi \partial_r \rho + \rho \partial^2_r \phi & = 0.
     \label{eq:NS_1D}
\end{split}
\end{equation}
We can integrate the first equation using the fact that the compressibility is negligible \cite{leighton2007derivation}.
\begin{equation}
    \int_{r_\infty}^{r} \frac{\partial}{\partial r'} \left[ \frac{\partial \phi}{\partial t} +\frac{1}{2} \left( \frac{\partial \phi}{\partial r'} \right)^2 \right] dr' = - \frac{1}{\rho} \int_{r_\infty}^{r} \frac{\partial p}{\partial r'} dr'
\end{equation}
On the left side, we take the velocity to vanish at infinity. On the right side, we assume that only the static and driving pressures, $p_\infty$ and $P(t)$ respectively, are relevant so that \cite{prosperetti1999old,prosperetti1986bubble,leighton2007derivation} 
\begin{equation}
    \partial_t \phi + \frac{1}{2}\left( \partial_r \phi \right)^2 = \frac{(p_\infty+P(t))-p(t,r)}{\rho}.
    \label{eq:press_vel}
\end{equation}
Eq. \ref{eq:press_vel} gives the pressure at coordinate $(r,t)$ in terms of the velocity of the fluid, the density, and the applied pressure.
